---
title: "Week 13 - Part I - Functional programming with Purrr - Continued"
author: "Jose Luis Rodriguez Gil"
date: "29/11/2022"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: cosmo
    highlight: tango
    number_sections: true
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
library(tidyverse)
library(janitor)
library(here)

library(fs) # Series of tools to work with fyle-systems

```

```{r my theme, include=FALSE}

source(here("functions", "theme_pepe_full.R"))

theme_set(theme_pepe_full())  #Sets the theme for all ggplot plots in this .Rmd file (no need to call it in the plot itself)

```


## Example III - Using purrr to load multiple files at once

The approach we are going to take is to create a tibble with a column named `files` where we will list the address of all files contained in our target folder (in this case the `data` folder).

After that, we will use `map()` to iterate through that list and read each of the files, then we will bind the rows to have one single file.

```{r}

combined_data <- tibble(files = fs::dir_ls(here("data", "batches"))) %>%  # we create a tibble of files in that folder. Remember we are in an .Rmd file, so we need to use here()
  mutate(data = pmap(list(files), 
                     ~ read_csv(..1, col_names = TRUE))) %>%  # We load each individual file as a tibble-within-a-tibble
  select(data) %>% # select only the actual data tibbles
  map_df(bind_rows) %>%  # bind them all into one tibble
  clean_names() # clean the column names

combined_data

```

What if we wanted to keep important information stored in the file name (e.g. the batch number in this case)?

```{r}

combined_data <- tibble(files = fs::dir_ls(here("data", "batches"))) %>%  # we create a tibble of files in that folder
  mutate(data = pmap(list(files), 
                     ~ read_csv(..1, col_names = TRUE))) %>%  # We load each individual file as a tibble-within-a-tibble
  mutate(data = pmap(list(files, data), 
                     ~ mutate(..2, source_file = as.character(..1)))) %>% # To each individual dataset we add the name of the file it came from (for reference)
  select(data) %>% # select only the actual data tibbles
  map_df(bind_rows) %>%  # bind them all into one tibble
  clean_names() # clean the column names

combined_data

```

Now we can use what we know of working with strings to get the batch numbe rinto its own column.

```{r}

combined_data %>% 
  mutate(batch = stringr::str_extract(source_file, "(?<=Batch_)[:digit:]{1}")) %>% # extract the date using regex
  select(-source_file) # we dont need it anymore

```



